### 2017-03-15 readme.Rmd
update readme

$\lambda(z) = \tilde \lambda(z) \cdot s(z)$

@@

$pr(y=0) = exp(-s(z)*A)$

@@

$pr( y=1) = 1-pr(y=0)$
         $= 1-exp(-s(z)*A)$

@@

Now that we have estimated $s(z)$ we can use it as an offset in the estimation of $\lambda(z)$. If we refer to Fithian and Hastie 2014, we can see back in section 2.5 *Identifiability and sampling bias* that $\lambda(z) = \tilde \lambda(z) \cdot s(z)$, so we can directly translate this into an offset within a model that aims to estimated the *observation process* for *Victaphanta lampra*. This is because:

$\lambda(x)=\exp^{\tilde \alpha + \tilde\beta^\prime x_1(z)} \exp^{\gamma^\prime + \delta x_2(x)}$

@@

par(mfrow=c(1,2))
plot(p_v_lampra_w_s_cell,col=jet.colors(100),main='accounting for sighting bias')
points(po_v_lampra,pch=16,cex=0.4,col=rgb(0, 0, 0, 0.3))
plot(p_v_lampra_wo_s_cell,col=jet.colors(100),main='ignoring sighting bias')
points(po_v_lampra,pch=16,cex=0.4,col=rgb(0, 0, 0, 0.3))

>>>>

$ \lambda(z) = \tilde \lambda(z) \cdot s(z)$

@@

$ pr(y=0) = exp(-s(z)*A) $

@@

$ pr( y=1) = 1-pr(y=0) $
         $ = 1-exp(-s(z)*A) $

@@

Now that we have estimated $s(z)$ we can use it as an offset in the estimation of $ \lambda(z)$. If we refer to Fithian and Hastie 2014, we can see back in section 2.5 *Identifiability and sampling bias* that $ \lambda(z) = \tilde \lambda(z) \cdot s(z)$, so we can directly translate this into an offset within a model that aims to estimated the *observation process* for *Victaphanta lampra*. This is because:

$ \lambda(x)= e^{\tilde \alpha + \tilde\beta^\prime x_1(z)} e^{\gamma^\prime + \delta x_2(x)}$

@@

par(mfrow=c(1,2),oma=c(4,4,4,4))
plot(p_v_lampra_w_s_cell,col=jet.colors(100),main='accounting for sighting bias')
points(po_v_lampra,pch=16,cex=0.4,col=rgb(0, 0, 0, 0.3))
plot(p_v_lampra_wo_s_cell,col=jet.colors(100),main='ignoring sighting bias')
points(po_v_lampra,pch=16,cex=0.4,col=rgb(0, 0, 0, 0.3))
